\LARGE \bf Informed sampling by Markov Chain Monte Carlo methods

### 2017-02-08 paper.tex
continue some mcmc

One of the popular classes of Monte Carlo simulation is 
\emph{Markov Chain Monte Carlo} (MCMC)~\cite{ADDJ03}.
Here, the samples are drawn by generating a Markov chain such that the distribution of points on the chain converges to the desired distribution.
The Markov Chain can be generated by performing a random walk such as
in Metropolis-Hastings~\cite{}
or Gibbs sampling~\cite{}.
Alternatively, samples on the chain can be generated by simulating Hamiltonian dynamics~\cite{} (instead of performing the random walk).
This approach, termed Hybrid or Hamiltonian Monte Carlo (HMC)~\cite{} was shown to converge faster to the desired distribution, when compared to random-walk based MCMC algorithms.

@@

\section{Algorithm}
\label{sec:algorithm}

>>>>

One of the popular classes of Monte Carlo simulation is 
\emph{Markov Chain Monte Carlo} (MCMC)~\cite{ADDJ03}.
Here, the samples are drawn by generating a Markov chain such that the distribution of points on the chain converges to the desired distribution.
The Markov Chain can be generated by performing a random walk such as
in Metropolis-Hastings~\cite{ADDJ03} or Gibbs sampling~\cite{ADDJ03}.
Alternatively, samples on the chain can be generated by simulating Hamiltonian dynamics~\cite{N11} (instead of performing the random walk).
This approach, termed Hybrid or Hamiltonian Monte Carlo (HMC)~\cite{N11} was shown to converge faster to the desired distribution, when compared to random-walk based MCMC algorithms.

@@

\dy{add a math description}

\section{Informed Sampling}
\label{sec:algorithm}
